Modal Abstractions for Virtualizing Memory Addresses

### 2023-04-12 examples.tex
+

One of the key tasks of a page fault handler in a general-purpose OS kernel is to map new pages into an address space by writing into an existing page table.

@@

$\specline{\textsf{P} \ast \mathcal{I}\texttt{ASpace}(\theta,\gammaPred,\rtv)  \ast  \texttt{r14}\mapsto_{r} \_ \ast \texttt{rdi}\mapsto_{r} \vaddr \ast \texttt{rax}\mapsto_{r} \_ \ast \ulcorner \texttt{aligned va} \land  \theta \; !!\; \texttt{maddr} = \texttt{None}\urcorner}_{\rtv}$

@@

\todo[inline]{emphasize the write to the L1 page table is validated by the fact that the identity mapping exists}

>>>>

One of the key tasks of a page fault handler in a general-purpose OS kernel is to map new pages into an address space by writing into an existing page table. To do so, we first allocate a fresh page, then calculate the appropriate known-valid page table walks and update the appropriate L1 page table entry.

@@

$\specline{\textsf{P} \ast \mathcal{I}\texttt{ASpace}(\theta,\gammaPred,\rtv)  \ast  \texttt{r14}\mapsto_{r} \_ \ast \texttt{rdi}\mapsto_{r} \vaddr \ast \texttt{rax}\mapsto_{r} \_ \ast \ulcorner \texttt{aligned va} \land  \theta \; !!\; \vaddr = \texttt{None}\urcorner}_{\rtv}$

@@

In Figure \ref{fig:mapping_code}, we see
%\todo[inline]{emphasize the write to the L1 page table is validated by the fact that the identity mapping exists}
